Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-05-13 manuscript.Rmd
switch to apa

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
author:
  - name: Aaron Peikert
    affil: a, b, c
    email: peikert@mpib-berlin.mpg.de
  - name: Andreas M. Brandmaier
    affil: a, b, d 
    email: brandmaier@mpib-berlin.mpg.de
affiliation:
  - num: a
    address: |
      Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany
  - num: b
    address: |
     Max Planck UCL Centre for Computational Psychiatry and Ageing Research Berlin, Germany and London, UK
  - num: c
    address: |
      Department of Psychology, Humboldt-Universität zu Berlin, Unter den Linden 6, 10117 Berlin, Germany
  - num: d
    address: |
      MSB Medical School Berlin, Rüdesheimer Str. 50, 14197 Berlin, Germany
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
    - apa.csl
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
  tlmgr:
    - pgf
    - preview
    - libertine
  apt:
    - git
    - rsync
    - curl
    - inkscape
output: rticles::tf_article
type: ARTICLE TEMPLATE
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; Bayesian; Open Science
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE
)
knitr::read_chunk("R/plots.R")

@@

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(getOption("tikzXelatexPackages"), "\\usepackage{amsfonts}", "\\usepackage{libertine}")
)
```

@@

```{r posterior-fig, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:posterior}Posterior probability (confirmation as firmness) as a function of theoretical risk $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

```{r other-measures-fig, dev = "tikz", cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:other-measures}Several measures for confirmation as an increase in firmness as a function of $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

@@

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
shorttitle: "The Objective of Preregistration"
author: 
  - name: Aaron Peikert
    affiliation: "1,2,3"
    email: peikert@mpib-berlin.mpg.de
    corresponding : yes    # Define only one corresponding author
    address: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
    role:
      - Conceptualization
      - Writing---Original Draft Preparation
      - Writing---Review & Editing
      - Methodology
      - Formal analysis
      - Software
      - Visualization
      - Project administration
  - name: Maximilian S. Ernst
    affiliation: "3"
    role:
      - Writing---Review & Editing
      - Formal analysis
      - Validation
  - name: Andreas M. Brandmaier
    affiliation: "1, 2, 4"
    role:
      - Writing---Review & Editing
      - Supervisions
affiliation:
  - id: 1
    institution: Max Planck Institute for Human Development
  - id: 2
    institution: Max Planck UCL Centre for Computational Psychiatry and Ageing Research
  - id: 3
    institution: Humboldt-Universität zu Berlin
  - id: 4
    institution: MSB Medical School Berlin
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; Bayesian; Open Science
wordcount         : "`r tryCatch(wordcountaddin::word_count(), error = function(x)'~7000')`"
figsintext: false
figurelist: false
tablelist : false
footnotelist: false
lineno: true
linkcolor: "blue"
csquotes: false
class: "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
header-includes:
  - \raggedbottom
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
    - apa.csl
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
    - crsh/papaja@1c488f7
  tlmgr:
    - apa6
    - pgf
    - preview
  apt:
    - git
    - rsync
    - curl
    - inkscape
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  dev = "tikz"
)
knitr::read_chunk("R/plots.R")

@@

options(
  tikzDefaultEngine = "xetex",
  tikzXelatexPackages = c(getOption("tikzXelatexPackages"), "\\usepackage{amsfonts}")
)
```

@@

```{r posterior-fig, cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:posterior}Posterior probability (confirmation as firmness) as a function of theoretical risk $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

```{r other-measures-fig, cache=TRUE, warning=FALSE}
#| fig.cap: "\\label{fig:other-measures}Several measures for confirmation as an increase in firmness as a function of $\\tau$, where $\\tau$ is either certain (solid line) or maximally uncertain (dotted line)."

@@

\newpage

@@

::: {#refs custom-style="Bibliography"}
:::
